LAGOS lake depth

### 2020-01-10 figures/01_contrasts.Rmd
add reservoir classifications

```{r 01_contrasts_depth, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.height = 3.5}
theme_opts <- theme(axis.text.x = element_text(angle = 90))

cowplot::plot_grid(gg_depth_shape_class + 
                     theme_opts, 
                   gg_depth_conny_class + 
                     theme_opts +
                     theme(axis.title.y = element_blank()), 
                   gg_depth_glaciated_class + 
                     theme_opts +
                     theme(axis.title.y = element_blank()), 
                   nrow = 1)
```

@@

```{r glaciated_vs_shapeclass, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
dt_sub <- dplyr::filter(dt, !is.na(shape_class), shape_class != "neither")
as.data.frame(
  table(paste(dt_sub$lake_glaciatedlatewisc, dt_sub$shape_class))) %>%
  tidyr::separate(Var1, c("glaciation", "shape_class"), sep = " ") %>%
  ggplot() + 
  geom_point(aes(glaciation, shape_class, size = Freq)) +
  scale_size_continuous(range = c(5, 20)) +
  theme(legend.position = "none")
```

>>>>

```{r gg_depth_reservoir, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}

gg_depth_reservoir <- dt %>%
  dplyr::filter(!is.na(reservoir_class)) %>%
  group_by(reservoir_class) %>%
  summarize(lake_maxdepth_m = list(tibble::enframe(
    quantile(lake_maxdepth_m, probs = c(0.05,0.5,0.95), na.rm = TRUE)))) %>% 
  unnest() %>%
  tidyr::spread(name, value) %>%
  ggplot() +
geom_pointrange(aes(x = reservoir_class, y = `50%`, 
                      ymin = `5%`, ymax = `95%`)) +
  ylab("Depth (m)") + xlab("")
```

```{r gg_depth_xtabs, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
dt_sub <- dplyr::filter(dt, 
                        !is.na(shape_class), shape_class != "neither", 
                        !is.na(reservoir_class))
# group_by(dt_sub, lake_glaciatedlatewisc, reservoir_class) %>%
#   tally() %>%
#   arrange(lake_glaciatedlatewisc) %>%
#   gridExtra::grid.table()

gg_depth_xtabs <- group_by(dt_sub, 
                           lake_glaciatedlatewisc, reservoir_class) %>%
    summarize(lake_maxdepth_m = list(tibble::enframe(
    quantile(lake_maxdepth_m, probs = c(0.05,0.5,0.95), na.rm = TRUE)))) %>% 
  unnest() %>%
  tidyr::spread(name, value) %>%
  tidyr::unite(cat, lake_glaciatedlatewisc:reservoir_class) %>%
  ggplot() +
geom_pointrange(aes(x = cat, y = `50%`, 
                      ymin = `5%`, ymax = `95%`)) +
  ylab("Depth (m)") + xlab("")

```

```{r 01_contrasts_depth, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.height = 6}
theme_opts <- theme(axis.text.x = element_text(angle = 90))

cowplot::plot_grid(  
cowplot::plot_grid(gg_depth_shape_class + 
                     theme_opts, 
                   gg_depth_conny_class + 
                     theme_opts +
                     theme(axis.title.y = element_blank()), 
                   gg_depth_glaciated_class + 
                     theme_opts +
                     theme(axis.title.y = element_blank()), 
                   gg_depth_reservoir + 
                     theme_opts +
                     theme(axis.title.y = element_blank()), 
                   nrow = 1), 
cowplot::plot_grid(gg_depth_xtabs + theme_opts, 
                   ggplot() + geom_blank() + 
                     theme(panel.background = element_blank()), nrow = 1), 
nrow = 2)

```

@@

```{r gg_tally_glaciated_vs_shapeclass, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
dt_sub <- dplyr::filter(dt, !is.na(shape_class), shape_class != "neither")
as.data.frame(
  table(paste(dt_sub$lake_glaciatedlatewisc, dt_sub$shape_class))) %>%
  tidyr::separate(Var1, c("glaciation", "shape_class"), sep = " ") %>%
  ggplot() + 
  geom_point(aes(glaciation, shape_class, size = Freq)) +
  scale_size_continuous(range = c(5, 20)) +
  theme(legend.position = "none")
```
